 1.
   ```{r}
   x = sample(c(2,4,8,16), size = 10000, prob=c(0.2,0.3,0.1,0.4), replace=TRUE)
   hist(x)
   ```


   Note: given that we are dealing with a discrete distribution, 
   a contingency table might be a better choice:

   ```{r echo=FALSE}
   library(kableExtra)
   kable(t(table(x))) %>% 
      kable_styling(full_width = FALSE)
   ```


 2. 
    We apply the function $\sin$ to the simulations. The histogram of the obtained values is going to be a good (graphical) approximation to the pdf of the transformed random variable:


    ```{r}
    x = rexp(100000)
    y = sin(x)
    hist(y)
```


 3. 
    Having learned that histograms look like the pdfs of the underlying distributions, we draw the histogram:


    ```{r}
    x = rcauchy(10000)
    y = atan(x) * 2/pi
    hist(y)
    ```


    It looks uniform (if we replace $10,000$ by
    $100,000$&\leq \hsig_t +  it will look even more uniform). We
    conclude that $2/\pi \arctan(X)$ is probably uniformly
    distributed on $(-1,1)$. Hence,  $Y = \arctan(X)$ is probably
    uniformly distributed on $(-\pi/2, \pi/2)$. 

